Verifying Demonstrations

### 2018-05-31 paper/conclusions.tex
Highlights contribution of DB anon creds

>>>>

Of separate interest, we can now provide distance bounding for authenticating 
more general attributes than provided by previous \ac{DB} protocols.
All privacy-preserving \ac{DB} protocols have so far focused on identity-based 
authentication, but not authentication of general attributes, as is the case 
for anonymous credentials.
With our contribution, Alice can now prove more complex statements to Bob, \eg 
that she is older than 18 but younger than 40 without revealing her actual age,  
and at the same time Bob can be sure that Alice is not just relaying messages 
from her older sister Carol.

### 2018-05-31 paper/intro.tex
Highlights contribution of DB anon creds

Our second contribution is an adaptation of the Schnorr's protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr's protocol in the \ac{ZKPK} used in anonymous credentials. 
%Seb: I have put the following sentence because due to the amount of current work recently in distance-bounding, I believe that our sentence should be made more reasonable 
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.

\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}) as well as a discussion of the performance and implementation issues (\cref{PerformanceAnalysis}). 
Finally, we conclude with a discussion and futures works in \cref{Conclusion}.

>>>>

Our second contribution is an adaptation of the Schnorr's protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr's protocol in the 
\ac{ZKPK} used in anonymous credentials and thus we are, to the best of our 
knowledge, the first to provide \ac{DB} anonymous credentials.

\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}) as well as a discussion of the performance and implementation issues (\cref{PerformanceAnalysis}). 
Finally, we conclude with a discussion and future works in \cref{Conclusion}.
